---
title: "Plotting decodeCC exp1"
author: "Yu-Chin Chiu"
date: "June 15, 2017"
output: md_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width=6, fig.height=4, fig.path='figure/',
                      include = TRUE, warning=FALSE, message=FALSE)
```

#### First, Set up the environment and load the data: step3_gpSummary.Rda
```{r set up, include=FALSE}
rm(list=ls())
library(tidyverse)  # to use ggplot 
currentDir <-  getwd()
setwd(currentDir)
load("~/YCCProjects/decodeCC/analysis/step3_gpSummary.Rda")
```

#### Set up some formating for the plots
Set up some good format, here i am using apatheme with white background for figure 1a, with black axis lines, no grids.
Default theme is good for visual comparison (theme_gray() with white grid lines, gray background), used for others here.

```{r fig apa-format, echo = FALSE}
apatheme = theme_bw()+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.line=element_line())
dodge = position_dodge(width=0.9)
```
## Stroop Task
### 1a. Plot the 2 block type x 2 trial type CSPC effect: RT
```{r CSPC_RT}
levels(CSPC$trialType) <- c("Congruent", "Incongruent")
levels(CSPC$blockType) <- c("Rarely InCongruent", "Freq. InCongruent")

CSPC %>%
  ggplot(aes(x = blockType, y = gpmeanRT, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanRT + (1*SE_rt), ymin = gpmeanRT - (1*SE_rt)), 
                position = dodge, width = .25) + 
  apatheme + 
  ylab("mean RT (Stroop)") +
  coord_cartesian(ylim=c(550,700)) +
  scale_fill_grey()

```

Alternatively, can use geom_bar(stat='identity', position = dodge) in lieu of goem_col(poistion = dodge). 
The default of geom_bar is count, but the default for geom_col is 'identity' (data)

### 1b. Plot the 2 half x 2 block type x 2 trial type CSPC effect: RT
```{r CSPC_RT2}
levels(CSPC_half$half)      <- c("First Half", "Second Half")
levels(CSPC_half$blockType) <- c("Rarely InCongruent", "Freq. InCongruent")
levels(CSPC_half$trialType) <- c("Congruent", "Incongruent")

CSPC_half %>%
  ggplot(aes(x = blockType, y = gpmeanRT, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanRT + (1*SE_rt), ymin = gpmeanRT - (1*SE_rt)), 
                position = dodge, width = .25) + 
  facet_grid(.~half) + 
  ylab("mean RT (Stroop)") +
  coord_cartesian(ylim = c(550,700)) +
  scale_fill_grey() 

```

### 2.Plot the 2 block type x 2 trial type CSPC effect: ACC
```{r CSPC_ACC}
CSPC %>%
  ggplot(aes(x = blockType, y = gpmeanACC, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanACC + (1*SE_acc), ymin = gpmeanACC - (1*SE_acc)), 
                position = dodge, width = .25) + 
  ylab("mean ACC (Stroop)") +
  coord_cartesian(ylim=c(80,100)) +
  scale_fill_grey()
```

### 3a.Plot the 2 block type x 2 trial type ISSP effect: RT
```{r ISSP_RT}
levels(ISSP$trialType) <- c("Repeat", "Switch")
levels(ISSP$swProb)    <- c("Rarely switching", "Freq. switching")

ISSP %>%
  ggplot(aes(x = swProb, y = gpmeanRT, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanRT + (1*SE_rt), ymin = gpmeanRT - (1*SE_rt)), 
                position = dodge, width = .25) + 
  ylab("mean RT (task-switching)") +
  coord_cartesian(ylim=c(550,700)) +
  scale_fill_grey()


```

### 3b.Plot the 2 half x 2 block type x 2 trial type ISSP effect: RT
```{r ISSP_RT2}
levels(ISSP_half$trialType) <- c("Repeat", "Switch")
levels(ISSP_half$swProb) <- c("Rarely switching", "Freq. switching")
levels(ISSP_half$half) <- c("First half", "Second half")

ISSP_half %>%
  ggplot(aes(x = swProb, y = gpmeanRT, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanRT + (1*SE_rt), ymin = gpmeanRT - (1*SE_rt)), 
                position = dodge, width = .25) + 
  facet_grid(.~half) + 
  ylab("mean RT (task-switching)") +
  coord_cartesian(ylim=c(550,700)) +
  scale_fill_grey()
```

### 4.Plot the 2 block type x 2 trial type ISSP effect: ACC
```{r ISSP_ACC}
ISSP %>%
  ggplot(aes(x = swProb, y = gpmeanACC, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanACC + (1*SE_acc), ymin = gpmeanACC - (1*SE_acc)), 
                position = dodge, width = .25) + 
  ylab("mean ACC (task-switching)") +
  coord_cartesian(ylim=c(65,100)) +
  scale_fill_grey()
```

## Memory Recognition Task
### 5a.Plot the memory performance as a function of control context previously (2 block type x 2 trial type) in the Stroop task
```{r recogM}
levels(recogM$trialType) <- c("Congruent", "Incongruent","New")
levels(recogM$blockType) <- c("Rarely InCongruent", "Freq. InCongruent", "New")

recogM %>%
  ggplot(aes(x = blockType, y = gpmeanACC, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanACC + (1*SE_acc), ymin = gpmeanACC - (1*SE_acc)), 
                position = dodge, width = .25) + 
  ylab("mean ACC (memory)") +
  coord_cartesian(ylim=c(50,80)) +
  scale_fill_grey()

```

### 5b.Plot the memory performance as a function of control context previously (2 half x 2 block type x 2 trial type) in the Stroop task
```{r recogM2}
levels(recogM_half$trialType) <- c("Congruent", "Incongruent", "New")
levels(recogM_half$blockType) <- c("Rarely InCongruent", "Freq. InCongruent", "New")
levels(recogM_half$half)      <- c("New", "First Half", "Second Half")

recogM_half %>%
  ggplot(aes(x = blockType, y = gpmeanACC, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanACC + (1*SE_acc), ymin = gpmeanACC - (1*SE_acc)), 
                position = dodge, width = .25) + 
  facet_grid(.~half) + 
  ylab("mean ACC (memory)") +
  coord_cartesian(ylim=c(50,80)) +
  scale_fill_grey()

```

### 6.Plot the RT for memory task as a function of control context previously (2 block type x 2 trial type) in the Stroop task
```{r memRT}
recogM %>%
  ggplot(aes(x = blockType, y = gpmeanRT, fill = trialType))  +
  geom_col(position = dodge) + 
  geom_errorbar(aes(ymax = gpmeanRT + (1*SE_rt), ymin = gpmeanRT - (1*SE_rt)), 
                position = dodge, width = .25) + 
  ylab("mean RT (memory)") +
  coord_cartesian(ylim=c(800,1000)) +
  scale_fill_grey()

```

### 7.Scatter plot (CSPC vs. ISSP) to see if there is any relationship bw two effects: 
```{r CSPCvsISSP}
gpBasic %>%
  ggplot(mapping = aes(x = ISSP, y = CSPC)) + 
  geom_point() + 
  geom_smooth(method=lm)

```

No correlation so far, p = 

```{r pearsonR}
cor(gpBasic$CSPC, gpBasic$ISSP)
 
```
